Sparse Function Space Representation of Neural Networks for Adaption and Retention

### 2023-05-10 paper/main.tex
started the NN section

\textbf{Neural Network in weight space}

@@

%Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$. Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.

The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
\begin{equation} 
   \vlambda = [ \MKzz + \vbeta]\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
   \vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
\label{eq:dual_sparse}
\end{equation}

@@

The key quantities we need to build our sparse GP are $(\alpha_i, \beta_i)$ and a kernel function $\kappa$

>>>>

\textbf{Neural Network} A neural network takes ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ and fits a function $f(\mathbf{x}_{i};\transitionParams)$ through the following optimization:
\begin{align} \label{eq-empirical-risk}
  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{P}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{P}} \left(
  \sum_{i=1}^{N} l(f(\mathbf{x}_{i} ; \transitionParams), y_i) + \frac{1}{\delta}R(\transitionParams)  \right).
\end{align}
If $l(f(\mathbf{x}_{i} ; \transitionParams), y_i) = -\log(p(y \mid f(\mathbf{x}_{i}))$

@@

Here, $\MKzz$ to denote the $m \times m$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
\begin{equation} 
   \vlambda = [ \MKzz + \vbeta]\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
   \vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
\label{eq:dual_sparse}
\end{equation}

@@

The key quantities we need to build our sparse GP are $(\alpha_i, \beta_i)$ and a kernel function $\kappa$  and from that we are able to make predictions and variance estimates. Crucially in the dual formulation our posterior contains all the training data given the sum in \cref{eq:dual_sparse}.
